---
title: "Exp_1_inferential_control"
author: "Nadine Balbach"
date: "9/7/2022"
output: html_document
---


# Include relevant packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("devtools")
# install.packages("cli")
# library(cli)
#devtools::install_github("dosc91/SfL", upgrade_dependencies = TRUE)
# install.packages("cli")
library(tidyr)
library(ggplot2)
library(gridExtra)
library(trimr)
library(lme4)
library(lmerTest)
#library(sjPlot)
library(Rmisc)
library(dplyr)
library(ggbreak)
library(reshape2)
library(stringr)
library(rlang)
library(naniar)
library(LMERConvenienceFunctions)
library(betareg)
#library(SfL)
#library(performance)

```

## import functions, set plot directory, clear global environment
```{r}
rm(list=ls())
#tiny bug concerning return value fixed in sdTrim from trimr
#TODO: maybe use devtools
source("sdTrimBugFixed.R")
plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)
```

### load data
```{r}
load("trimmedData.RData")

```
### descriptive statistics for rts
```{r}
rt_aggregated<-aggregate(resid_rt~quantifier, data=trimmed_data_exp1_judge_control_only, mean)
ses_rt<-aggregate(resid_rt~quantifier, data=trimmed_data_exp1_judge_control_only, function(x) {sd(x)/sqrt(length(x))})
rt_aggregated<-cbind(rt_aggregated,ses_rt[,2])
```
### descriptive statistics for acc
```{r}
control_agg_acc <- aggregate(correct~quantifier+model, data=trimmed_data_exp1_judge_control_only, function(x) {c(sum(x),length(x),100*mean(x),100*sd(x)/sqrt(length(x)))})
control_agg_acc
```

### inferential statistics
### judgements with logit mixed effect regression analysis (glmer - binomial logit - NB: step function not available!)

## prep data
```{r}
trimmed_data_exp1_judge_control_only$quantifier <- as.factor(trimmed_data_exp1_judge_control_only$quantifier)
trimmed_data_exp1_judge_control_only$quantifier <- relevel(trimmed_data_exp1_judge_control_only$quantifier, "at_most_one")
```
### glmer analysis
```{r}
glmer_exp1_control_global <- glmer(correct ~ quantifier + (quantifier | participant_id) + (quantifier|item), data = trimmed_data_exp1_judge_control_only, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see help('isSingular')

summary(glmer_exp1_control_global)
#quantifier no compared to reference level highly significant, no other significance

glmer_exp1_control_global_m0 <- glmer(correct ~ (quantifier | participant_id) + (quantifier|item), data = trimmed_data_exp1_judge_control_only, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see help('isSingular')

anova(glmer_exp1_control_global, glmer_exp1_control_global_m0)
#with quantifier significantly better
```

### check for best random interecept
```{r}

# check whether item as random effect makes a difference
nullGlmermdl_control<-glmer(correct~ (1|participant_id) + (1 |item), data = trimmed_data_exp1_judge_control_only,family = binomial(link = "logit"))
null2Glmermdl_control<-glmer(correct~ (1|participant_id), data = trimmed_data_exp1_judge_control_only, family = binomial(link = "logit"))
anova(nullGlmermdl_control, null2Glmermdl_control)

# could leave out item in random effects structure

```

### glmer analysis without item
```{r}
glmer_exp1_control_global2 <- glmer(correct ~ quantifier + (quantifier | participant_id), data = trimmed_data_exp1_judge_control_only, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see help('isSingular')

summary(glmer_exp1_control_global2)
#quantifier 'no' compared to reference level highly significant, no other significance, but tendency for exactly one

glmer_exp1_control_global_m02 <- glmer(correct ~ (quantifier | participant_id), data = trimmed_data_exp1_judge_control_only, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see help('isSingular')

anova(glmer_exp1_control_global2, glmer_exp1_control_global_m02)
#with quantifier highly significantly better
```

##picture RT

### distribution Check (NB: do we have to account for the missing values in resid_rt?)

```{r}


shapiro.test(trimmed_data_exp1_judge_control_only$resid_rt)
# nicht normalverteilt
trimmed_data_exp1_judge_control_only$logResidRT <- log(trimmed_data_exp1_judge_control_only$resid_rt)
#NaNs produced
shapiro.test(trimmed_data_exp1_judge_control_only$logResidRT)
#immer noch nicht normalverteilt

plot(density(trimmed_data_exp1_judge_control_only$resid_rt))
#plot(density(trimmed_data_exp1_judge_control_only$logResidRT))
#Error in density.default(trimmed_data_exp1_judge_control_only$logResidRT) : 'x' contains missing values

```

###full model
```{r}
full_lmerMdl_control <- lmer(resid_rt ~ quantifier + (quantifier | participant_id) + (quantifier|item), data = trimmed_data_exp1_judge_control_only, REML = FALSE)
#boundary (singular) fit: see help('isSingular')
```

### check whether item as random effect makes a difference
```{r}

nullcontrol_Lmermdl<-lmer(resid_rt~ (1|participant_id) + (1 |item), data = trimmed_data_exp1_judge_control_only, REML = FALSE)
              
null2_control_Lmermdl<-lmer(resid_rt~ (1|participant_id), data = trimmed_data_exp1_judge_control_only, REML = FALSE)
anova(nullcontrol_Lmermdl, null2_control_Lmermdl)

# could leave out item in random effects structure
```


#find best model
```{r}

# full model without item
full_lmerMdl_control <- lmer(resid_rt ~ quantifier + (quantifier | participant_id), data = trimmed_data_exp1_judge_control_only, REML = FALSE)
#boundary (singular) fit: see help('isSingular')
step(full_lmerMdl_control)

#best model: resid_rt ~ quantifier + (1 | participant_id)
trimmed_data_exp1_judge_control_only <- within(trimmed_data_exp1_judge_control_only, quantifier <- relevel(quantifier, ref = "no"))
#continuing with best model
best_lmerMdl_control <- lmer(resid_rt ~ quantifier + (1| participant_id), data = trimmed_data_exp1_judge_control_only, REML = FALSE)

summary(best_lmerMdl_control)

#slight effect for at_least_one vs. at_most_one?
```

### check homoscedasticity
#### not met, run a Welch t-statistic
```{r}
var.test(trimmed_data_exp1_judge_control_only$resid_rt, trimmed_data_exp1_judge_excl_control$resid_rt)
```

### t test

```{r}
t_test  <- t.test(trimmed_data_exp1_judge_control_only$resid_rt, trimmed_data_exp1_judge_excl_control$resid_rt,var.equal = FALSE)
t_test$estimate + t_test$conf.int[1]
t_test$estimate - t_test$conf.int[1]
```

### model comparison
```{r}
full_lmerMdl_control <- lmer(resid_rt ~ quantifier + (quantifier | participant_id), data = trimmed_data_exp1_judge_control_only, REML = FALSE)
full_lmerMdl_control_m0 <- lmer(resid_rt ~ 1 + (quantifier | participant_id), data = trimmed_data_exp1_judge_control_only, REML = FALSE)
```
```{r}
anova(full_lmerMdl_control,full_lmerMdl_control_m0)
```


