---
title: "Exp_1_descriptive"
author: "Nadine Balbach"
date: "9/1/2022"
output: html_document
---


# Include relevant packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("devtools")
# install.packages("cli")
library(cli)
# devtools::install_github("dosc91/SfL", upgrade_dependencies = TRUE)
# install.packages("cli")
library(tidyr)
library(ggplot2)
library(gridExtra)
library(trimr)
library(lme4)
library(lmerTest)
library(dplyr)
library(ggbreak)
library(Rmisc)
library(reshape2)
library(stringr)
library(rlang)
library(naniar)
library(LMERConvenienceFunctions)
library(betareg)
#library(SfL)
library(performance)
#library(sjPlot)
```

## import functions, set plot directory, clear global environment
```{r}
rm(list=ls())
#tiny bug concerning return value fixed in sdTrim from trimr
#TODO: maybe use devtools
source("sdTrimBugFixed.R")
source("appendRdata.R")
plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)
```


### load data
```{r}
load("trimmedData.RData")

```

### name quantifiers, Exp1
```{r}
trimmed_data_exp1 <- trimmed_data_exp1 %>% 
  mutate(quantifier = case_when(cond == 2 | cond == 6 | cond == 10 | cond == 14 ~ "no",
                                   cond == 4 | cond == 8 | cond == 12 | cond == 16 ~ "at_most_one",
                                   cond == 1 | cond == 5 | cond == 9 | cond == 13 ~ "exactly_one",
                                   cond == 3 | cond == 7 | cond == 11 | cond == 15 ~ "at_least_one"))
```

### name empty set property, Exp1
```{r}
trimmed_data_exp1 <- trimmed_data_exp1 %>% 
  mutate(empty_set = case_when(cond == 2 | cond == 6 | cond == 10 | cond == 14 ~ "es",
                                   cond == 4 | cond == 8 | cond == 12 | cond == 16 ~ "es",
                                   cond == 1 | cond == 5 | cond == 9 | cond == 13 ~ "non_es",
                                   cond == 3 | cond == 7 | cond == 11 | cond == 15 ~ "non_es"))
```

### name quantifier classes, Exp1 
```{r}

trimmed_data_exp1 <- trimmed_data_exp1 %>% 
  mutate(quantifier_type = case_when(cond == 2 | cond == 6 | cond == 10 | cond == 14 ~ "non-degree",
                                cond == 4 | cond == 8 | cond == 12 | cond == 16 ~ "degree",
                                cond == 1 | cond == 5 | cond == 9 | cond == 13 ~ "non-degree",
                                cond == 3 | cond == 7 | cond == 11 | cond == 15 ~ "degree"))
```

### encode models
```{r}
trimmed_data_exp1$model <- ifelse(trimmed_data_exp1$model == "1", "0,n",
                                        ifelse(trimmed_data_exp1$model == "1,1", "1,n", 
                                               ifelse(trimmed_data_exp1$model == "1,2", "2,n",
                                                      ifelse(trimmed_data_exp1$model == "0,1", "0,m 1,n",
                                                             ifelse(trimmed_data_exp1$model == "0", "0,m 0,n", "0,m 2,n")))))
```




### descriptive stats judgements, Exp 1
### estimate random effect and compute pseudo residuals
```{r}
trimmed_data_fillers_judge <- subset(trimmed_data_fillers, roi=="pictureRT")
trimmed_data_fillers_judge$quantifier <- str_split(trimmed_data_fillers_judge$sentence, " ", n = 2, simplify = TRUE)[,1]
appendRData(trimmed_data_fillers_judge, file = "trimmedData.RData")

resp_lmer <- lmer(rt~response+(1+response|participant_id), data=trimmed_data_fillers_judge)
isSingular(resp_lmer)

#compute pseudo residuals
trimmed_data_exp1_judge <- subset(trimmed_data_exp1, roi=="pictureRT")
trimmed_data_exp1_judge$response_num <- ifelse(trimmed_data_exp1_judge$response == "True", 1, 0)
trimmed_data_exp1_judge$resid_rt <- trimmed_data_exp1_judge$rt - 
  (ranef(resp_lmer)$participant_id[trimmed_data_exp1_judge$participant_id,1] + 
     trimmed_data_exp1_judge$response_num *
     (fixef(resp_lmer)[2]+
        ranef(resp_lmer)$participant_id[trimmed_data_exp1_judge$participant_id,2])) 

with(trimmed_data_exp1_judge, plot(rt, resid_rt, col = participant_id))

```

### descriptive stats judgement stage, Exp 1

### excluding the 4 controls
```{r}
trimmed_data_exp1_judge_excl_control <- subset(trimmed_data_exp1_judge, trimmed_data_exp1_judge$cond < 13)

#controls only
trimmed_data_exp1_judge_control_only <- subset(trimmed_data_exp1_judge, trimmed_data_exp1_judge$cond > 12)

#save for inferential stats
appendRData(trimmed_data_exp1_judge_excl_control,
     file = "trimmedData.RData")
appendRData(trimmed_data_exp1_judge_control_only,
     file = "trimmedData.RData")
```

#### means and CIs
```{r}
rt_aggregated<-aggregate(resid_rt~quantifier+model, data=trimmed_data_exp1_judge_excl_control, mean)
```

#### compute ses
```{r}
ses_rt<-aggregate(resid_rt~quantifier+model, data=trimmed_data_exp1_judge_excl_control, function(x) {sd(x)/sqrt(length(x))})
rt_aggregated<-cbind(rt_aggregated,ses_rt[,3])
```



#### names, labels, encoding...
```{r}
names(rt_aggregated)<-c("quantifier", "model", "pictureRT", "se")
#rt_aggregated$roi<-as.factor(rt_aggregated$roi)
rt_aggregated$model<-as.factor(rt_aggregated$model)
```


#### do a plot of the RTs
```{r}
gp_rt <- ggplot(rt_aggregated, aes(x=quantifier, y=pictureRT, fill=model, group=model))+
  geom_col(position = "dodge")+ geom_errorbar(aes(ymin=pictureRT-se, ymax=pictureRT+se), width=.2,
                 position=position_dodge(.9)) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reading time in ms\n(and std. errors)")+
  #scale_x_discrete(labels=c("Außer dem markierten","ist","QUANTIFIER","weiteres", "Dreieck","rot."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))#+
  #facet_grid(~model)
gp_rt
ggsave(file.path(plots_dir,"mean_judgment_rt_exp1.pdf"), device="pdf", width=14, height=5)
```

### accuracy by quant and model 
```{r}
## accuracy per condition absolute (N correct trials and total N of trials) 
## and relative in percent (means and standard errors of the mean)
agg_acc <- aggregate(correct~quantifier+model, data=trimmed_data_exp1_judge_excl_control, function(x) {c(sum(x),length(x),100*mean(x),100*sd(x)/sqrt(length(x)))})
agg_acc

## acc for controls
control_agg_acc <- aggregate(correct~quantifier+model, data=trimmed_data_exp1_judge_control_only, function(x) {c(sum(x),length(x),100*mean(x),100*sd(x)/sqrt(length(x)))})
control_agg_acc

```

### GLMER analysis judgments

```{r}
# sum coding of factors
trimmed_data_exp1_judge_excl_control$empty_set <- as.factor(trimmed_data_exp1_judge_excl_control$empty_set)
trimmed_data_exp1_judge_excl_control$quantifier_type <- as.factor(trimmed_data_exp1_judge_excl_control$quantifier_type)
trimmed_data_exp1_judge_excl_control$model <- as.factor(trimmed_data_exp1_judge_excl_control$model)

contrasts(trimmed_data_exp1_judge_excl_control$empty_set) =contr.sum(2)
contrasts(trimmed_data_exp1_judge_excl_control$quantifier_type) =contr.sum(2)
contrasts(trimmed_data_exp1_judge_excl_control$model) =contr.sum(3)

glmer_exp1_global <- glmer(correct ~ empty_set*quantifier_type*model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_global)

glmer_exp1_global_m0 <- glmer(correct ~ empty_set*quantifier_type+empty_set*model + quantifier_type*model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

anova(glmer_exp1_global, glmer_exp1_global_m0)

## break down three-way interaction effects: separate analyses for degree and non-degree quantifiers

trimmed_data_exp1_judge_excl_control_degree <- subset(trimmed_data_exp1_judge_excl_control, quantifier_type == "degree")

trimmed_data_exp1_judge_excl_control_non_degree <- subset(trimmed_data_exp1_judge_excl_control, quantifier_type == "non-degree")

## degree quantifiers: sign. two-way interactions

glmer_exp1_degree <- glmer(correct ~ empty_set*model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_degree)

glmer_exp1_degree_m0 <- glmer(correct ~ empty_set+model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

anova(glmer_exp1_degree,glmer_exp1_degree_m0)

## non-degree quantifiers: no sign. differences except for the first two-way interaction

glmer_exp1_non_degree <- glmer(correct ~ empty_set*model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_non_degree)

glmer_exp1_non_degree_m0 <- glmer(correct ~ empty_set+model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

anova(glmer_exp1_non_degree,glmer_exp1_non_degree_m0)
```

### LMER analysis judgment RTs

```{r}
## no three-way interaction for judgment RTs

lmer_exp1_judge_rt_global_m1 <- lmer(resid_rt ~ empty_set*quantifier_type*model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control, REML = FALSE)

lmer_exp1_judge_rt_global_m2 <- lmer(resid_rt ~ empty_set*quantifier_type+empty_set*model + quantifier_type*model  + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control, REML = FALSE)

anova(lmer_exp1_judge_rt_global_m1,lmer_exp1_judge_rt_global_m2)

summary(lmer_exp1_judge_rt_global_m2)

## sign. two-way interactions between empty-set quantifiers and models: 
## empty-set quantifiers differ from non-empty-set quantifiers with respect 
## to 0-models but show similar RTs for 1- and 2-models

lmer_exp1_judge_rt_global_m3 <- lmer(resid_rt ~ empty_set*quantifier_type + quantifier_type*model  + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control, REML = FALSE)

anova(lmer_exp1_judge_rt_global_m2,lmer_exp1_judge_rt_global_m3)
```

### descriptive stats reading stage, Exp 1

#### means and CIs
```{r}
trimmed_data_exp1_read <- subset(trimmed_data_exp1, roi!="pictureRT")
trimmed_data_exp1_read_excl_control <- subset(trimmed_data_exp1_read, trimmed_data_exp1_read$cond < 13)
trimmed_data_exp1_read_control_only <- subset(trimmed_data_exp1_read, trimmed_data_exp1_read$cond > 12)


### do rt residuals here as well?
#save for inferential stats
appendRData(trimmed_data_exp1_read_excl_control,
     file = "trimmedData.RData")
appendRData(trimmed_data_exp1_read_control_only,
     file = "trimmedData.RData")

rt_aggregated<-aggregate(rt~quantifier+roi, data=trimmed_data_exp1_read_excl_control, mean)
```


### TODO: find another way to compute ses (SEwithin?)
```{r}
ses_rt<-aggregate(rt~quantifier+roi, data=trimmed_data_exp1_read_excl_control, function(x) {sd(x)/sqrt(length(x))})
rt_aggregated<-cbind(rt_aggregated,ses_rt[,3])
```

#### names, labels, encoding...
```{r}
names(rt_aggregated)<-c("quantifier", "roi", "sentenceRT", "se")
rt_aggregated$roi<-as.factor(rt_aggregated$roi)
```


### do a plot of the sentence RTs
```{r}
plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)

gp_rt <- ggplot(rt_aggregated, aes(x=roi, y=sentenceRT, colour=quantifier, group=quantifier))+
  geom_line()+ geom_point()+
  geom_ribbon(aes(ymin=sentenceRT-se, ymax=sentenceRT+se), linetype=0, alpha=0.1)+
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reading time in ms\n(and std. errors)")+
  scale_x_discrete(labels=c("Außer dem markierten","ist","QUANTIFIER","weiteres", "Dreieck","rot."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))
gp_rt
ggsave(file.path(plots_dir,"mean_sentence_rt_exp1.pdf"), device="pdf", width=28, height=5)
```


