---
title: "Exp_1_inferential_stats"
author: "Nadine Balbach"
date: "9/1/2022"
output: html_document
---

# Include relevant packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("devtools")
# install.packages("cli")
# library(cli)
#devtools::install_github("dosc91/SfL", upgrade_dependencies = TRUE)
# install.packages("cli")
library(tidyr)
library(ggplot2)
library(gridExtra)
library(trimr)
library(lme4)
library(lmerTest)
#library(sjPlot)
library(Rmisc)
library(dplyr)
library(ggbreak)
library(reshape2)
library(stringr)
library(rlang)
library(naniar)
library(LMERConvenienceFunctions)
library(betareg)
#library(SfL)
#library(performance)

```

## import functions, set plot directory, clear global environment
```{r}
rm(list=ls())
#tiny bug concerning return value fixed in sdTrim from trimr
#TODO: maybe use devtools
source("sdTrimBugFixed.R")
plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)
```

### load data
```{r}
load("trimmedData.RData")

```

### inferential statistics
### judgements with logit mixed effect regression analysis (glmer - binomial logit - NB: step function not available!)

## prep data
```{r}
trimmed_data_exp1_judge_excl_control$degree_quantifier <- as.factor(trimmed_data_exp1_judge_excl_control$degree_quantifier)
trimmed_data_exp1_judge_excl_control$model_judge <- as.factor(trimmed_data_exp1_judge_excl_control$model_judge)
trimmed_data_exp1_judge_excl_control$model <- as.factor(trimmed_data_exp1_judge_excl_control$model)
trimmed_data_exp1_judge_excl_control$model <- relevel(trimmed_data_exp1_judge_excl_control$model, ref = "1-model")

trimmed_data_exp1_judge_excl_control$empty_set_quantifier <- as.factor(trimmed_data_exp1_judge_excl_control$empty_set_quantifier)

#contrasts
contrasts(trimmed_data_exp1_judge_excl_control$empty_set_quantifier) =contr.sum(2)
contrasts(trimmed_data_exp1_judge_excl_control$degree_quantifier) =contr.sum(2)
contrasts(trimmed_data_exp1_judge_excl_control$model_judge) =contr.sum(2)
contrasts(trimmed_data_exp1_judge_excl_control$model) =contr.sum(3)

```

### glmer analysis
```{r}
glmer_exp1_global <- glmer(correct ~ empty_set_quantifier*degree_quantifier*model_judge + (1 + model| participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_global)

glmer_exp1_global_m0 <- glmer(correct ~ empty_set_quantifier*degree_quantifier+empty_set_quantifier*model_judge + degree_quantifier*model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

anova(glmer_exp1_global, glmer_exp1_global_m0)

#three way-interaction significant
```

## break down three-way interaction effect: separate analyses for degree and non-degree quantifiers

### subset data
```{r}
trimmed_data_exp1_judge_excl_control_degree <- subset(trimmed_data_exp1_judge_excl_control, degree_quantifier == "yes")

trimmed_data_exp1_judge_excl_control_non_degree <- subset(trimmed_data_exp1_judge_excl_control, degree_quantifier == "no")

```

### glms degree / non-degree
```{r}
glmer_exp1_degree <- glmer(correct ~ empty_set_quantifier*model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_degree)

#highly significant two-way interaction

glmer_exp1_degree_m0 <- glmer(correct ~ empty_set_quantifier+model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_degree_m0)

anova(glmer_exp1_degree,glmer_exp1_degree_m0)
#m0 worse

#non-degree
glmer_exp1_non_degree <- glmer(correct ~ empty_set_quantifier*model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))
summary(glmer_exp1_non_degree)
#slightly significant two-way interaction only for non-degree

glmer_exp1_non_degree_m0 <- glmer(correct ~ empty_set_quantifier+model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))


anova(glmer_exp1_non_degree,glmer_exp1_non_degree_m0)
# m0 slightly worse
```

## break down two-way interactions: seperate for empty-set vs. non-empty-set

### subset data
```{r}
trimmed_data_exp1_judge_excl_control_degree_es <- subset(trimmed_data_exp1_judge_excl_control_degree, empty_set_quantifier == "yes")

trimmed_data_exp1_judge_excl_control_degree_nes <- subset(trimmed_data_exp1_judge_excl_control_degree, empty_set_quantifier == "no")

trimmed_data_exp1_judge_excl_control_non_degree_es <- subset(trimmed_data_exp1_judge_excl_control_non_degree, empty_set_quantifier == "yes")

trimmed_data_exp1_judge_excl_control_non_degree_nes <- subset(trimmed_data_exp1_judge_excl_control_non_degree, empty_set_quantifier == "no")

```

### glmerss degree empty_set / non-empty-set
```{r}

#degree es (at most)
glmer_exp1_degree_es <- glmer(correct ~ model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree_es, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_degree_es)
#significant

#degree nes (at least)

glmer_exp1_degree_nes <- glmer(correct ~ model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree_nes, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_degree_nes)
#significant 

```

### glmerss non-degree empty_set / non-empty-set
```{r}

#non-degree es (no)
glmer_exp1_non_degree_es <- glmer(correct ~ model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree_es, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_non_degree_es)
#not significant

#non-degree nes (exactly one)

glmer_exp1_non_degree_nes <- glmer(correct ~ model_judge + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree_nes, family = binomial(link = "logit"), control = glmerControl(optimizer="bobyqa"))

summary(glmer_exp1_non_degree_nes)
#slightly significant 

```

### multicollinearity check
```{r}

# correlation_matrix(data = trimmed_data_exp1_judge_excl_control,
#                    variables = c("degree_quantifier", "empty_set_quantifier", "model", "participant_id", "item"))
# -> no correlation

# check_collinearity(glmer_exp1_global)
# col_model <- check_collinearity(glmer_exp1_global)
# plot(col_model)

```



### check for best random interecept
```{r}

# check whether item as random effect makes a difference
nullGlmermdl<-glmer(correct~ (1|participant_id) + (1 |item), data = trimmed_data_exp1_judge_excl_control,family = binomial(link = "logit"))
null2Glmermdl<-glmer(correct~ (1|participant_id), data = trimmed_data_exp1_judge_excl_control, family = binomial(link = "logit"))
anova(nullGlmermdl, null2Glmermdl)

# should keep item in random effects structure

```







## picture RTs 
### distribution Check (NB: do we have to account for the missing values in resid_rt?)

```{r}


shapiro.test(trimmed_data_exp1_judge_excl_control$resid_rt)
# nicht normalverteilt
trimmed_data_exp1_judge_excl_control$logResidRT <- log(trimmed_data_exp1_judge_excl_control$resid_rt)
shapiro.test(trimmed_data_exp1_judge_excl_control$logResidRT)
#immer noch nicht normalverteilt

plot(density(trimmed_data_exp1_judge_excl_control$resid_rt))
#plot(density(trimmed_data_exp1_judge_excl_control$logResidRT))
#Error in density.default(trimmed_data_exp1_judge_excl_control$logResidRT) : 'x' contains missing values

```
### check NA 
There are negative value in residual RTs, because their responses are "no", and for "no" responses a part of rts will be subtracted. It can lead to negative values.
```{r}
na_index <- which(is.na(trimmed_data_exp1_judge_excl_control$logResidRT) == TRUE)
trimmed_data_exp1_judge_excl_control[na_index,]

plot(density(trimmed_data_exp1_judge_excl_control$logResidRT))
```
### ... and remove NAs
```{r}
trimmed_data_exp1_judge_excl_control <- trimmed_data_exp1_judge_excl_control %>% filter(!is.na(trimmed_data_exp1_judge_excl_control$logResidRT))
plot(density(trimmed_data_exp1_judge_excl_control$logResidRT))
# still not normal
```

### full model
```{r}
lmerMdl_full <- lmer(logResidRT ~ degree_quantifier*empty_set_quantifier*model + (1 + model| participant_id) + (1|item),data = trimmed_data_exp1_judge_excl_control, REML=F, lmerControl(optimizer="bobyqa"))

```

### multicollinearity check
```{r}

# correlation_matrix(data = trimmed_data_exp1_judge_excl_control,
#                    variables = c("degree_quantifier", "empty_set_quantifier", "model", "participant_id", "item"))
# no correlation

# check_collinearity(lmerMdl_full)
# 
# col_lmerModel <- check_collinearity(lmerMdl_full)
# plot(col_lmerModel)

```

# check whether item as random effect makes a difference
```{r}

nullLmermdl<-lmer(resid_rt~ (1|participant_id) + (1 |item), data = trimmed_data_exp1_judge_excl_control, REML = FALSE)
null2Lmermdl<-lmer(resid_rt~ (1|participant_id), data = trimmed_data_exp1_judge_excl_control, REML = FALSE)
anova(nullLmermdl, null2Lmermdl)

# should keep item in random effects structure
```

### model comparision full vs remove three way interactiton
```{r}
lmerMdl_full_m1 <- update(lmerMdl_full, .~.-degree_quantifier:empty_set_quantifier:model)
anova(lmerMdl_full_m1,lmerMdl_full)
```

### check for best model
```{r}
step(lmerMdl_full)
#best model is full model: resid_rt ~ degree_quantifier * empty_set_quantifier * model + (1 | participant_id) + (1 | item)

```


### significance & predictor strength
```{r}

anova(lmerMdl_full)


#try whether interaction and random slope possible to include
# strength <- predictor_strength(dependent = "resid_rt",
#                    fixed = c("degree_quantifier", "empty_set_quantifier", "model", "degree_quantifier:empty_set_quantifier", "empty_set_quantifier:model"),
#                    random_str = c("( 1 | participant_id)", "(1 | item)"),
#                    data = trimmed_data_exp1_judge_excl_control)
# strength[order(strength$R2m),]

#R2m -> marginal R-squared value - the higher the more variance is explained by the model and it's predictors in regard to the fixed effects
# -> empty-set quantifier & degree_quantifier best, followed by quantifier and lastly model

#R2c -> conditional R-squared value - the higher the more variance is explained by the model and it's predictors in regard to the fixed effects + random effects
# -> empty-set quantifier & degree_quantifier best, followed by quantifier and lastly model

```

### summary
```{r}

contrasts(trimmed_data_exp1_judge_excl_control$model)
summary(lmerMdl_full)

## significant three way interecation, two highly sign. two-way interactions between empty-set quantifiers and models: 
## empty-set quantifiers differ from non-empty-set quantifiers with respect 
## to 1- and 2-models (note that 1 and two do not correspond to the respective models, but to the comparisons) and two-way interaction between degree-quantifier and empty-set-quantifier, degree-quantifiers differ from non-degree quantifiers with respect to emty-set quantifiers
## no two-way interaction between degree-quantifier and model, but tendency for first comparison (1 vs. 0)

# fixef(lmerMdl_full)
# ranef(lmerMdl_full)
# confint(lmerMdl_full)
# plogis(7.06071514)

```


## break down three way interaction
### lmers degree / non-degree
```{r}

lmer_exp1_degree <- lmer(resid_rt ~ empty_set_quantifier*model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree, REML=F, lmerControl(optimizer="bobyqa"))  



summary(lmer_exp1_degree)
step(lmer_exp1_degree)

#highly significant two two-way interactions

# lmer_exp1_degree_m0 <- lmer(resid_rt ~ empty_set_quantifier+model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree, REML=F, lmerControl(optimizer="bobyqa"))
# 
# summary(lmer_exp1_degree_m0)
# 
# anova(lmer_exp1_degree,lmer_exp1_degree_m0)
#m0 worse

#non-degree
```
### model comparison removing significant two way interaction between es quantifier and model in degree 
```{r}
lmer_exp1_degree_m1 <- update(lmer_exp1_degree , .~.-empty_set_quantifier:model)
anova(lmer_exp1_degree_m1,lmer_exp1_degree )
```


### non degree
```{r}
lmer_exp1_non_degree <- lmer(resid_rt ~ empty_set_quantifier*model + (1+model|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree, REML=F, lmerControl(optimizer="bobyqa"))
summary(lmer_exp1_non_degree)
step(lmer_exp1_non_degree)
anova(lmer_exp1_non_degree)
#non-degree highly significant two-way interaction for second comparison of empty-set*model (empty-set=1, model=2 vs.1)

lmer_exp1_non_degree_m0 <- lmer(resid_rt ~ empty_set_quantifier+model + (1+model|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree, REML=F, lmerControl(optimizer="bobyqa"))
summary(lmer_exp1_non_degree_m0)

anova(lmer_exp1_non_degree,lmer_exp1_non_degree_m0)
# m0 worse
```


### lmers degree empty_set / non-empty-set
```{r}

#degree es (at most)

lmer_exp1_degree_es <- lmer(resid_rt ~ model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree_es, REML=F, lmerControl(optimizer="bobyqa"))
summary(lmer_exp1_degree_es)
# model1 vs. 0 highly sign.
#model  2 vs 1 high

#degree nes (at least)

lmer_exp1_degree_nes <- lmer(resid_rt ~ model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_degree_nes, REML=F, lmerControl(optimizer="bobyqa"))
summary(lmer_exp1_degree_nes)
#highly signif. for second model comparison (1 vs. 2)



```

### lmers non_degree empty_set / non-empty-set
```{r}

#non-degree es (no)

lmer_exp1_non_degree_es <- lmer(resid_rt ~ model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree_es, REML=F, lmerControl(optimizer="bobyqa"))
summary(lmer_exp1_non_degree_es)
# highly signif. for both model comparisons ( 1 vs 0, 2 vs 1)


#non-degree nes (exactly one)

lmer_exp1_non_degree_nes <- lmer(resid_rt ~ model + (1|participant_id) + (1|item), data = trimmed_data_exp1_judge_excl_control_non_degree_nes, REML=F, lmerControl(optimizer="bobyqa"))
summary(lmer_exp1_non_degree_nes)
#model comparison 2 (1 vs 2) slightly significant 



```


## Tukey Contrasts
### check whether levels of predictors are significantly different
```{r}
# tukey(model = lmerMdl_full,
#       predictor = degree_quantifier)
# 
# tukey(model = lmerMdl_full,
#       predictor = empty_set_quantifier)
# 
# tukey(model = lmerMdl_full,
#       predictor = model)
```




# sentence RTs - inferential stats for penultimate and last region

## data prep
```{r}
trimmed_data_exp1_read_excl_control$degree_quantifier <- as.factor(trimmed_data_exp1_read_excl_control$degree_quantifier)
trimmed_data_exp1_read_excl_control$empty_set_quantifier <- as.factor(trimmed_data_exp1_read_excl_control$empty_set_quantifier)
trimmed_data_exp1_read_excl_control$model <- as.factor(trimmed_data_exp1_read_excl_control$model)
contrasts(trimmed_data_exp1_read_excl_control$empty_set_quantifier) =contr.sum(2)
contrasts(trimmed_data_exp1_read_excl_control$degree_quantifier) =contr.sum(2)
```



```{r}
# creating two data sets for the regions of interest
roi6_data <- subset(trimmed_data_exp1_read_excl_control, (roi == "rt_6_raw"))
roi5_data <- subset(trimmed_data_exp1_read_excl_control, (roi == "rt_5_raw"))
```

### distribution Check

```{r}
shapiro.test(roi6_data$rt)
# not normally distributed
roi6_data$logRt <- log(roi6_data$rt)
shapiro.test(roi6_data$logRt)
# not normally distributed


shapiro.test(roi5_data$rt)
# not normally distributed

roi5_data$logRt <- log(roi5_data$rt)
shapiro.test(roi5_data$logRt)
# not normally distributed

```

### full models
```{r}
Roi6LmerMdl_full <- lmer(logRt ~ empty_set_quantifier*degree_quantifier + (1 | participant_id) + (1 | item),
                  data = roi6_data, REML=F,
                  lmerControl(optimizer="bobyqa"))

Roi5LmerMdl_full <- lmer(logRt ~ empty_set_quantifier*degree_quantifier + (1 | participant_id) + (1 | item),
                  data = roi5_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
```


### multicollinearity check
## Roi 6
```{r}

# correlation_matrix(data = roi6_data,
#                    variables = c("degree_quantifier", "empty_set_quantifier", "participant_id", "item"))
#no correlation

# check_collinearity(Roi6LmerMdl_full)
# 
# 
# Roi6_col_model <- check_collinearity(Roi6LmerMdl_full)
# plot(Roi6_col_model)

```

## Roi 5
```{r}

# correlation_matrix(data = roi5_data,
#                    variables = c("degree_quantifier", "empty_set_quantifier", "participant_id", "item"))

#no correlation

# check_collinearity(Roi5LmerMdl_full)
# 
# 
# Roi5_col_model <- check_collinearity(Roi5LmerMdl_full)
# plot(Roi5_col_model)
```


### check for random intercept
## roi6
```{r}
# check whether item as random effect makes a difference 
nullLmermdl<-lmer(logRt~ (1|participant_id) + (1 |item), data = roi6_data, REML = FALSE)
null2Lmermdl<-lmer(logRt ~ (1|participant_id), data = roi6_data, REML = FALSE)
anova(nullLmermdl, null2Lmermdl)
#-> could leave item out 
```

## roi5
```{r}

# check whether item as random effect makes a difference 
nullLmermdl<-lmer(logRt~ (1|participant_id) + (1 |item), data = roi5_data, REML = FALSE)
null2Lmermdl<-lmer(logRt ~ (1|participant_id), data = roi5_data, REML = FALSE)
anova(nullLmermdl, null2Lmermdl)
#-> could leave item out

```

### leave out item in random effect structure


```{r}
Roi6LmerMdl_full <- lmer(logRt ~ empty_set_quantifier*degree_quantifier + (1 | participant_id),
                  data = roi6_data, REML=F,
                  lmerControl(optimizer="bobyqa"))

Roi5LmerMdl_full <- lmer(logRt ~ empty_set_quantifier*degree_quantifier + (1 | participant_id),
                  data = roi5_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
```

### check for best model
```{r}
step(Roi6LmerMdl_full)
#best model logRt ~ (1 | participant_id)
```

```{r}
step(Roi5LmerMdl_full)
# best model logRt ~ (1 | participant_id)

#!!!there is a trend for the empty_set_quantifier though in both
```

### significance & predictor strength
## roi 6
```{r}
anova(Roi6LmerMdl_full)

# strength <- predictor_strength(dependent = "logRt",
#                    fixed = c("degree_quantifier", "empty_set_quantifier"),
#                    random_str = c("( 1 | participant_id)"),
#                    data = roi6_data)
# strength[order(strength$R2m),]

# here for degree_quantifier 

#R2m -> marginal R-squared value - the higher the more variance is explained by the model and it's predictors in regard to the fixed effects
#R2c -> conditional R-squared value - the higher the more variance is explained by the model and it's predictors in regard to the fixed effects + random effects

### coefficients

summary(Roi6LmerMdl_full)

### Tukey Contrasts
# check whether levels of predictors are significantly different

# tukey(model = Roi6LmerMdl_full,
#       predictor = degree_quantifier)
# #not good
# 
# tukey(model = Roi6LmerMdl_full,
#       predictor = empty_set_quantifier)
# 
# #trend for empty_set quantifier
```

## roi 5
```{r}
anova(Roi5LmerMdl_full)

# strength <- predictor_strength(dependent = "logRt",
#                    fixed = c("degree_quantifier", "empty_set_quantifier"),
#                    random_str = c("( 1 | participant_id)"),
#                    data = roi5_data)
# strength[order(strength$R2m),]

#R2m -> marginal R-squared value - the higher the more variance is explained by the model and it's predictors in regard to the fixed effects
#R2c -> conditional R-squared value - the higher the more variance is explained by the model and it's predictors in regard to the fixed effects + random effects

#degree_quantifier better

### coefficients

summary(Roi5LmerMdl_full)

### Tukey Contrasts
# check whether levels of predictors are significantly different

# tukey(model = Roi5LmerMdl_full,
#       predictor = degree_quantifier)
# #nothing
# 
# tukey(model = Roi5LmerMdl_full,
#       predictor = empty_set_quantifier)

#trend for emty-set quantifier
```

#better models?

```{r}
Roi6LmerMdl_full <- lmer(logRt ~ empty_set_quantifier+degree_quantifier + (1 | participant_id),
                  data = roi6_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi6LmerMdl_full)

#trend for empty_set quantifier

Roi5LmerMdl_full <- lmer(logRt ~ empty_set_quantifier+degree_quantifier + (1 | participant_id),
                  data = roi5_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi5LmerMdl_full)

#trend for empty_set quantifier

Roi6LmerMdl_full2 <- lmer(logRt ~ empty_set_quantifier + (1 | participant_id),
                  data = roi6_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi6LmerMdl_full2)
#trend for empty_set quantifier

Roi5LmerMdl_full2 <- lmer(logRt ~ empty_set_quantifier + (1 | participant_id),
                  data = roi5_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi5LmerMdl_full2)
#trend for empty_set quantifier

Roi6LmerMdl_full3 <- lmer(logRt ~ degree_quantifier + (1 | participant_id),
                  data = roi6_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi6LmerMdl_full3)
#nothing

Roi5LmerMdl_full3 <- lmer(logRt ~ degree_quantifier + (1 | participant_id),
                  data = roi5_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi5LmerMdl_full3)
#nothing

Roi5LmerMdl_null <- lmer(logRt ~ (1 | participant_id),
                  data = roi5_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi5LmerMdl_null)

Roi6LmerMdl_null <- lmer(logRt ~ (1 | participant_id),
                  data = roi6_data, REML=F,
                  lmerControl(optimizer="bobyqa"))
summary(Roi5LmerMdl_null)

anova(Roi6LmerMdl_full, Roi6LmerMdl_full2)
anova(Roi6LmerMdl_full2, Roi6LmerMdl_null)
#-> lmer-model with empty-set quantifier slightly better

anova(Roi5LmerMdl_full, Roi5LmerMdl_full2)
anova(Roi5LmerMdl_full2, Roi5LmerMdl_null)
#-> lmer-model with empty-set quantifier slightly better

#there only seems to be a trend for the factor empty_set_quantifier for both regions

```
# check random structures
```{r}
lmerMdl_full <- lmer(log(resid_rt) ~ degree_quantifier*empty_set_quantifier*model + (1 | participant_id) + (1|item),data = trimmed_data_exp1_judge_excl_control, REML=F, lmerControl(optimizer="bobyqa"))

# use this model as the best model
lmerMdl_full_1 <- update(lmerMdl_full, .~.- (1| participant_id) - (1| item)+ (1 + model| participant_id)+(1 + model|item))

```
add random slope for model
```{r}
lmerMdl_full_1 <- update(lmerMdl_full, .~.- (1| participant_id) - (1| item)+ (1 + model| participant_id)+(1 + model|item))
anova(lmerMdl_full,lmerMdl_full_1)
step(lmerMdl_full_1)
```
```{r}
lmerMdl_best <- lmer(log(resid_rt) ~ degree_quantifier*empty_set_quantifier*model + (1 + model| participant_id) + (1|item),data = trimmed_data_exp1_judge_excl_control, REML=F, lmerControl(optimizer="bobyqa"))
lmerMdl_best_1 <- update(lmerMdl_best, .~.-degree_quantifier:empty_set_quantifier:model)
anova(lmerMdl_best,lmerMdl_best_1)
```


