---
title: "Exp_2_descriptive"
author: "Nadine Balbach"
date: "9/1/2022"
output: html_document
---


# Include relevant packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("devtools")
# install.packages("cli")
library(cli)
devtools::install_github("dosc91/SfL", upgrade_dependencies = TRUE)
# install.packages("cli")
library(tidyr)
library(ggplot2)
library(gridExtra)
library(trimr)
library(lme4)
library(lmerTest)
library(sjPlot)
library(dplyr)
library(ggbreak)
library(Rmisc)
library(reshape2)
library(stringr)
library(rlang)
library(naniar)
library(LMERConvenienceFunctions)
library(betareg)
library(SfL)
library(performance)

```

## import functions, set plot directory, clear global environment
```{r}
rm(list=ls())
#tiny bug concerning return value fixed in sdTrim from trimr
#TODO: maybe use devtools
source("sdTrimBugFixed.R")
source("appendRdata.R")
plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)
```

### load data
```{r}
load("trimmedData.RData")
```

### descriptive stats judgements, Exp 2

### add correct es-quantifier labeling and model info

```{r}
trimmed_data_exp2 <- trimmed_data_exp2 %>% 
  mutate(empty_set_quantifier = case_when(cond == 1 | cond == 2 | cond == 3 | cond == 4 ~ "yes",
                                cond == 5 | cond == 6 | cond == 7 | cond == 8 ~ "no"))
```

### add model and quantifier labeling
```{r}
trimmed_data_exp2$model <- ifelse(trimmed_data_exp2$cond %in% c(1,5), "0,n",
                                        ifelse(trimmed_data_exp2$cond %in% c(2,6),"1,n",
                                                ifelse(trimmed_data_exp2$cond %in% c(3,7),"2,n", "3,n")))

trimmed_data_exp2$quantifier <- ifelse(trimmed_data_exp2$cond %in% c(1:4), "at_most_two", "exactly_two")
```

#### estimate random effect and compute pseudo residuals
```{r}
#compute pseudo residuals
trimmed_data_exp2_judge <- subset(trimmed_data_exp2, roi=="pictureRT")

resp_lmer <- lmer(rt~response+(1+response|participant_id), data=trimmed_data_fillers_judge)
isSingular(resp_lmer) #(NB: should we deal with the singularity?)

trimmed_data_exp2_judge$response_num <- ifelse(trimmed_data_exp2_judge$response == "True", 1, 0)
trimmed_data_exp2_judge$resid_rt <- trimmed_data_exp2_judge$rt - 
  (ranef(resp_lmer)$participant_id[trimmed_data_exp2_judge$participant_id,1] + 
     trimmed_data_exp2_judge$response_num *
     (fixef(resp_lmer)[2]+
        ranef(resp_lmer)$participant_id[trimmed_data_exp2_judge$participant_id,2])) 

with(trimmed_data_exp2_judge, plot(rt, resid_rt, col = participant_id))

appendRData(trimmed_data_exp2_judge,
     file = "trimmedData.RData")

#TODO: use residuals from exp 1 (+x) instead
```


### accuracy by quant and model 
```{r}
agg_acc <- aggregate(correct~quantifier+model, data=trimmed_data_exp2_judge, function(x) {c(mean(x),sd(x)/sqrt(length(x)))})
agg_acc

# worst for at_most and 0,n -> 0,47 vs. 0,89 and also a difference for 1,n -> 0,71 vs. 0,92

```


### means and CIs
```{r}
rt_aggregated<-aggregate(resid_rt~quantifier+model, data=trimmed_data_exp2_judge, mean)
```

#### TODO: find another way to compute ses (SEwithin?)
```{r}
ses_rt<-aggregate(resid_rt~quantifier+model, data=trimmed_data_exp2_judge, function(x) {sd(x)/sqrt(length(x))})
rt_aggregated<-cbind(rt_aggregated,ses_rt[,3])
```

#### names, labels, encoding...
```{r}
rt_aggregated<-cbind(rt_aggregated, agg_acc[,3])
names(rt_aggregated)<-c("quantifier", "model", "pictureRT", "se", "correct", "wrong")
#rt_aggregated$roi<-as.factor(rt_aggregated$roi)
rt_aggregated$model<-as.factor(rt_aggregated$model)
```


#### do a plot of the RTs
```{r}
gp_rt <- ggplot(rt_aggregated, aes(x=quantifier, y=pictureRT, fill=model, group=model))+
  geom_col(position = "dodge")+ geom_errorbar(aes(ymin=pictureRT-se, ymax=pictureRT+se), width=.2,
                 position=position_dodge(.9)) +
  geom_text(aes(label = round(correct,digits=2), x=quantifier, y=pictureRT), position = position_dodge(width = .9), vjust = -0.9, size=4, colour= "red")+
  labs(tag = "accuracy")+
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("residual reaction time in ms\n(and std. errors)")+
  #scale_x_discrete(labels=c("Außer dem markierten","ist","QUANTIFIER","weiteres", "Dreieck","rot."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))+
  theme(plot.tag.position=c(.95, .85))+
  theme(plot.tag= element_text(size=9, colour = "red"))
  #facet_grid(~model)
gp_rt
ggsave(file.path(plots_dir,"mean_judgment_rt_exp2.pdf"), device="pdf", width=14, height=5)
```




### descriptive stats reading, Exp 2

#### means and CIs
```{r}
trimmed_data_exp2_read <- subset(trimmed_data_exp2, roi!="pictureRT")
trimmed_data_exp2_read_excl_control <- subset(trimmed_data_exp2_read, trimmed_data_exp2_read$cond < 13)
trimmed_data_exp2_read_control_only <- subset(trimmed_data_exp2_read, trimmed_data_exp2_read$cond > 12)

#save for inferential stats
appendRData(trimmed_data_exp2_read,
     file = "trimmedData.RData")

rt_aggregated<-aggregate(rt~quantifier+roi, data=trimmed_data_exp2_read, mean)
```


### TODO: find another way to compute ses (SEwithin?)
```{r}
ses_rt<-aggregate(rt~quantifier+roi, data=trimmed_data_exp2_read, function(x) {sd(x)/sqrt(length(x))})
rt_aggregated<-cbind(rt_aggregated,ses_rt[,3])
```

#### names, labels, encoding...
```{r}
names(rt_aggregated)<-c("quantifier", "roi", "sentenceRT", "se")
rt_aggregated$roi<-as.factor(rt_aggregated$roi)
```


### do a plot of the sentence RTs
```{r}
gp_rt <- ggplot(rt_aggregated, aes(x=roi, y=sentenceRT, colour=quantifier, group=quantifier))+
  geom_line()+ geom_point()+
  geom_ribbon(aes(ymin=sentenceRT-se, ymax=sentenceRT+se), linetype=0, alpha=0.1)+
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reading time in ms\n(and std. errors)")+
  scale_x_discrete(labels=c("Außer QUANTIFIER","sind","alle Kreise", "blau.")) +
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))
gp_rt
ggsave(file.path(plots_dir,"mean_sentence_rt_exp2_1.pdf"), device="pdf", width=28, height=5)

gp_rt <- ggplot(rt_aggregated, aes(x=quantifier, y=sentenceRT, fill=roi, group=roi))+
  geom_col(position = "dodge")+ geom_errorbar(aes(ymin=sentenceRT-se, ymax=sentenceRT+se), width=.2,
                 position=position_dodge(.9)) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reading time in ms\n(and std. errors)")+
  ####NB: check whether it is actually ms
  #scale_x_discrete(labels=c("Außer dem markierten","ist","QUANTIFIER","weiteres", "Dreieck","rot."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))
gp_rt

ggsave(file.path(plots_dir,"mean_sentence_rt_exp2_2.pdf"), device="pdf", width=28, height=5)
```