---
title: "Exp_3_descriptive"
author: "Nadine Balbach"
date: "9/1/2022"
output: html_document
---
  
  
# Include relevant packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("devtools")
# install.packages("cli")
library(cli)
# devtools::install_github("dosc91/SfL", upgrade_dependencies = TRUE)
# install.packages("cli")
library(tidyr)
library(ggplot2)
library(gridExtra)
library(trimr)
library(lme4)
library(lmerTest)
library(sjPlot)
library(dplyr)
library(ggbreak)
library(Rmisc)
library(reshape2)
library(stringr)
library(rlang)
library(naniar)
library(LMERConvenienceFunctions)
library(betareg)
library(SfL)
library(performance)
```

## import functions, set plot directory, clear global environment
```{r}
rm(list=ls())
#tiny bug concerning return value fixed in sdTrim from trimr
#TODO: maybe use devtools
source("sdTrimBugFixed.R")
source("appendRdata.R")
plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)
```


### load data
```{r}
load("trimmedData.RData")

```

### name quantifier
```{r}
trimmed_data_exp3 <- trimmed_data_exp3 %>% 
  mutate(quantifier = case_when(cond == 1 | cond == 2 | cond == 7 | cond == 8 ~ "no",
                                cond == 3 | cond == 4 | cond == 5 | cond == 6 ~ "all"))
```

### name position
```{r}
trimmed_data_exp3 <- trimmed_data_exp3 %>% 
  mutate(position = case_when(cond == 1 | cond == 2 | cond == 3 | cond == 4 ~ "außer_beginning",
                                cond == 5 | cond == 6 | cond == 7 | cond == 8 ~ "außer_after_quant."))
```


### name model 
```{r}

trimmed_data_exp3 <- trimmed_data_exp3 %>% 
  mutate(model = case_when(cond == 1 | cond == 4 | cond == 6 | cond == 7 ~ "0,n",
                                       cond == 2 | cond == 3 | cond == 5 | cond == 8 ~ "4-5,n"))
         
```




### descriptive stats judgements
### estimate random effect and compute pseudo residuals
```{r}
trimmed_data_fillers_judge <- subset(trimmed_data_fillers, roi=="pictureRT")
trimmed_data_fillers_judge$quantifier <- str_split(trimmed_data_fillers_judge$sentence, " ", n = 2, simplify = TRUE)[,1]
appendRData(trimmed_data_fillers_judge, file = "trimmedData.RData")

resp_lmer <- lmer(rt~response+(1+response|participant_id), data=trimmed_data_fillers_judge)
isSingular(resp_lmer) #(NB: should we deal with the singularity?)

#compute pseudo residuals
trimmed_data_exp3_judge <- subset(trimmed_data_exp3, roi=="pictureRT")
trimmed_data_exp3_judge$response_num <- ifelse(trimmed_data_exp3_judge$response == "True", 1, 0)
trimmed_data_exp3_judge$resid_rt <- trimmed_data_exp3_judge$rt - 
  (ranef(resp_lmer)$participant_id[trimmed_data_exp3_judge$participant_id,1] + 
     trimmed_data_exp3_judge$response_num *
     (fixef(resp_lmer)[2]+
        ranef(resp_lmer)$participant_id[trimmed_data_exp3_judge$participant_id,2])) 

#save for inferential stats
appendRData(trimmed_data_exp3_judge,
            file = "trimmedData.RData")

with(trimmed_data_exp3_judge, plot(rt, resid_rt, col = participant_id))

#TODO: use residuals from exp 1 (+x) instead
```

### descriptive stats judge


### accuracy by quant and model 
```{r}
agg_acc <- aggregate(correct~quantifier+position+model, data=trimmed_data_exp3_judge, function(x) {c(mean(x),sd(x)/sqrt(length(x)))})
agg_acc

```


#### means and CIs
```{r}
rt_aggregated<-aggregate(resid_rt~quantifier+position+model, data=trimmed_data_exp3_judge, mean)
```

#### TODO: find another way to compute ses (SEwithin?) (NB: better use sds?)
```{r}
ses_rt<-aggregate(resid_rt~quantifier+position+model, data=trimmed_data_exp3_judge, function(x) {sd(x)/sqrt(length(x))})
rt_aggregated<-cbind(rt_aggregated,ses_rt[,4])
```



#### names, labels, encoding...
```{r}
#names(rt_aggregated)<-c("quantifier", "position", "model", "pictureRT", "se")
rt_aggregated<-cbind(rt_aggregated, agg_acc[,4])
names(rt_aggregated)<-c("quantifier", "position", "model", "pictureRT", "se", "correct", "wrong")

#rt_aggregated$roi<-as.factor(rt_aggregated$roi)
rt_aggregated$model<-as.factor(rt_aggregated$model)
```


#### do a plot of the RTs
```{r}
#change labels of grouping factor for facet_wrap

gp_rt <- ggplot(rt_aggregated, aes(x=quantifier, y=pictureRT, fill=model, group=model))+
  geom_col(position = "dodge")+ geom_errorbar(aes(ymin=pictureRT-se, ymax=pictureRT+se), width=.2,
                                              position=position_dodge(.9)) +
  geom_text(aes(label = round(correct,digits=2), x=quantifier, y=pictureRT), position = position_dodge(width = .9), vjust = -0.9, size=4, colour= "red")+
  labs(tag = "accuracy")+
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("residual reaction time in ms\n(and std. errors)")+
  ####NB: check whether it is actually ms
  #scale_x_discrete(labels=c("Außer dem markierten","ist","QUANTIFIER","weiteres", "Dreieck","rot."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))+
  theme(plot.tag.position=c(.95, .85))+
  theme(plot.tag= element_text(size=9, colour = "red"))+
  facet_wrap(~position, nrow = 1,scales = "free_x")
gp_rt
ggsave(file.path(plots_dir,"mean_judgment_rt_exp3.pdf"), device="pdf", width=14, height=5)
```



### descriptive stats reading, Exp 1

#### means and CIs
```{r}
trimmed_data_exp3_read <- subset(trimmed_data_exp3, roi!="pictureRT")

#save for inferential stats
appendRData(trimmed_data_exp3_read,
            file = "trimmedData.RData")

rt_aggregated<-aggregate(rt~quantifier+position+roi, data=trimmed_data_exp3_read, mean)
```


### TODO: find another way to compute ses (SEwithin?)
```{r}
ses_rt<-aggregate(rt~quantifier+position+roi, data=trimmed_data_exp3_read, function(x) {sd(x)/sqrt(length(x))})
rt_aggregated<-cbind(rt_aggregated,ses_rt[,4])
```

#### names, labels, encoding...
```{r}
names(rt_aggregated)<-c("quantifier", "position","roi", "sentenceRT", "se")
rt_aggregated$roi<-as.factor(rt_aggregated$roi)
```


### do a plot of the sentence RTs
```{r}
plots_dir<- file.path(getwd(),"plots")
if(!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE, showWarnings = FALSE)

# NB: since the items vary also in the position of the 'außer phrase' in a sentence, do we have to split them?
par(mfrow=c(2,2))
gp_rt <- ggplot(subset(rt_aggregated, position=="außer_beginning"), aes(x=roi, y=sentenceRT, colour=quantifier, group=quantifier))+
  geom_line()+ geom_point()+
  geom_ribbon(aes(ymin=sentenceRT-se, ymax=sentenceRT+se), linetype=0, alpha=0.1)+
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reading time in ms\n(and std. errors)")+
  scale_x_discrete(labels=c("Besides the marked","is/are","QUANTIFIER","red."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))
gp_rt

gp_rt <- ggplot(subset(rt_aggregated, position=="außer_after_quant."), aes(x=roi, y=sentenceRT, colour=quantifier, group=quantifier))+
  geom_line()+ geom_point()+
  geom_ribbon(aes(ymin=sentenceRT-se, ymax=sentenceRT+se), linetype=0, alpha=0.1)+
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reading time in ms\n(and std. errors)")+
  scale_x_discrete(labels=c("QUANTIFIER", "besides the marked","is/are","red."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))
gp_rt
ggsave(file.path(plots_dir,"mean_sentence_rt_exp3_1.pdf"), device="pdf", width=28, height=5)

gp_rt <- ggplot(subset(rt_aggregated, position=="außer_beginning"), aes(x=quantifier, y=sentenceRT, fill=roi, group=roi))+
  geom_col(position = "dodge")+ geom_errorbar(aes(ymin=sentenceRT-se, ymax=sentenceRT+se), width=.2,
                                              position=position_dodge(.9)) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reaction time in ms\n(and std. errors)")+
  ####NB: check whether it is actually ms
  #scale_x_discrete(labels=c("Außer dem markierten","ist","QUANTIFIER","weiteres", "Dreieck","rot."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))+
  facet_wrap(~position, nrow = 1,scales = "free_x")
gp_rt

gp_rt <- ggplot(subset(rt_aggregated, position=="außer_after_quant."), aes(x=quantifier, y=sentenceRT, fill=roi, group=roi))+
  geom_col(position = "dodge")+ geom_errorbar(aes(ymin=sentenceRT-se, ymax=sentenceRT+se), width=.2,
                                              position=position_dodge(.9)) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1), text = element_text(size=20))+
  #theme(axis.text.x = element_blank())+
  #ylim(210, 420)+
  ylab("reaction time in ms\n(and std. errors)")+
  ####NB: check whether it is actually ms
  #scale_x_discrete(labels=c("Außer dem markierten","ist","QUANTIFIER","weiteres", "Dreieck","rot."))+
  #theme(legend.position = c(0.68, 0.85), legend.title = element_blank())+
  theme(axis.title=element_text(size=16,face="bold"))+
  facet_wrap(~position, nrow = 1,scales = "free_x")
gp_rt


ggsave(file.path(plots_dir,"mean_sentence_rt_exp3_2.pdf"), device="pdf", width=28, height=5)
```


